The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Edit whatever text we have.

The class \texttt{VectorizedArray<Number>} is a key ingredient for the high
node-level performance of the matrix-free algorithms in deal.II~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper
class around a short vector of $n$ entries of type \texttt{Number} and maps
arithmetic operations to appropriate single-instruction/multiple-data (SIMD)
concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this release by making
it compatible with the STL algorithms found in the header \texttt{<algorithm>}.
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}.
Furthermore, the \texttt{VectorizedArray} class now supports range-based iterations over its entries.

Up to release 9.1, the
vector length $n$ has been set at compile time of the library to the highest
possible value supported by the given processor architecture.
Now, a second optional template argument
\texttt{VectorizedArray<Number, size>} can be given with \texttt{size} explicitly controlling
the vector length within the capabilities of a particular instruction set.
A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.

To account for the variable-size \texttt{VectorizedArray} class, all matrix-free related classes (like \texttt{MatrixFree} and \texttt{FEEvaluation})
have been extended with a new optional template argument specifying the
\texttt{VectorizedArrayType}. This allows users to select the vector length/ISA and,
as a consequence, the number of cells to be processed at once directly in their applications:
The deal.II-based
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order
discontinuous Galerkin methods (with more than a thousand degrees of freedom per cell), constructs a tensor product of two \texttt{MatrixFree} objects of different SIMD-vector
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

\begin{table}
\caption{Supported vector lengths of the class \texttt{VectorizedArray} and
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2/AltiVec \\
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\
\bottomrule
\end{tabular}

\caption{Comparison of relevant SIMD-related classes in deal.II and \texttt{C++23}.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (\texttt{C++23})} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

Furthermore, the new interfaces enable using any data structure
\texttt{VectorizedArrayType} as long as it supports required
functionalities like \texttt{size()} or \texttt{value\_type}. This prepares
for the \texttt{C++23} feature \texttt{std::simd} that will be enabled in the future.
Table~\ref{tab:simd} gives a comparison of the deal.II-specific SIMD classes and
the equivalent \texttt{C++23} classes. Finally, this change also prepares for specialized
code paths exploiting
vectorization within an element~\cite{KronbichlerKormann2019} in the future.

@@

For this release, the most noteworthy improvements for the GPU support are the
simplification of the kernel written by user, improvement of the error messages,
and overlapping of computation and communication when using CUDA-aware MPI with
the matrix-free framework. In order to simplify user code, we know recompute the
local degree of freedom and quadrature point indices instead of having the user
keeping track of them. A new option to overlap computation and communication is
now available when using CUDA-aware MPI and matrix-free. The underlying idea is
that only the degrees of freedom (dofs) on the boundary of the local domain
require communication. Before evaluating the matrix-free operator at these
degrees of freedom, we need to communicate the ghosted dofs from other
processors.  Similarly once the operator has been evaluated, we need to update
the resulting global vector with values from other processors. The strategy that
we are using consist in splitting the dofs in three groups: one group of dofs
that are on the local boundary and two groups each owning half of the interior
dofs. When evaluating the matrix-free operator, we start the MPI communication
to get the ghosted dofs and evaluate the operator on one of the two interior
dofs group. When the evaluation is done, we wait for the MPI to be over and
then, evaluate the operator on the boundary dofs group. When this evaluation is
over, we start the communication to update the global vector, we evaluate the
operator on the last of group of dofs, and finally wait for the MPI
communication to finish.

@@

Certain types of quantities in a simulation are constants fully known
at compile time. They can be pre-calculated and fully stored inside the
compiled program binary in order to avoid unnecessary initialization during
runtime. This optimization is now enabled for the class templates
\texttt{Tensor} and \texttt{SymmetricTensor} by qualifying their constructor,
member functions, and overloaded operators as \texttt{constexpr}.
For instance, the linear mechanical constitutive model for elastic solids
uses a constant fourth-order elasticity tensor
$\mathbb{C} = \lambda \boldsymbol{I} \otimes \boldsymbol{I} + 2 \mu \mathbb{I}$
which does not depend on the current state of strain.
This tensor can be statically initialized by defining it as
\texttt{constexpr SymmetricTensor<4, dim>}.
As another example, the lattice vectors in a crystal plasticity model are generally
constant and known during compilation time, enabling their efficient definition as
\texttt{constexpr Tensor<1, dim>}.
The capability of defining \texttt{constexpr} variables, functions, and methods
was introduced by the C++11 standard and was later expanded by the C++14 standard.
Therefore, the extent of \texttt{constexpr} support in \dealii{} depends on the C++
standard which is used to compile the library. The next release of \dealii{}
will fully adopt the features of the C++14 standard.

@@

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-47} solves the biharmonic equation with the
  clamped boundary condition. This program is based on the $C^0$ interior
  penalty method for fourth order problems. In order to overcome
  shortcomings of classical approaches, this method uses $C^0$ Lagrange finite
  elements and introduces ``jump`` and ``average`` on interfaces of elements.
  The resulting system is obtained through integration by parts, symmetrization,
  and stabilization. Appropriate choices for the penalty parameter are
  discussed based on numerical results.

@@

\item \texttt{step-58} is a program that solves the nonlinear
  Schr{\"o}dinger equation, which in non-dimensional form reads
  \begin{align*}
  - i \frac{\partial \psi}{\partial t}
  - \frac 12 \Delta \psi
  + V \psi
  + \kappa |\psi|^2 \psi
  &= 0,
  \end{align*}
  augmented by appropriate initial and boundary conditions and using
  an appropriate form for the potential $V=V(\mathbf x)$. The
  tutorial program focused on two specific aspects for which this
  equation serves as an excellent test case: (i) Solving
  complex-valued problems without splitting the equation into its
  real and imaginary parts (as \texttt{step-29} does, for
  example). (ii) Using operator splitting techniques. The equation is
  a particularly good test case for this technique because the only
  nonlinear term, $\kappa |\psi|^2 \psi$, does not contain any
  derivatives and consequently forms an ODE to be solved at each time
  step in an operator splitting scheme (for which, furthermore, there
  exists an analytic solution), whereas the remainder of the
  equation is linear and easily solved using standard finite element
  techniques.

@@

\begin{figure}
\renewcommand\figurename{Listing}

\centering

\begin{python}
import PyDealII.Release as dealii

@@

triangulation.execute_coarsening_and_refinement()
\end{python}

\includegraphics{python_mesh.png}

\caption{Python code that uses \texttt{deal.II}'s Python interface to generate a mesh shown at the bottom (coloured by the cell's material id).}
\label{python_wrapper}
\end{figure}

The initial support for Python has come in \texttt{deal.II 9.0}. The present release significantly extends the Python interface. Specifically, a large number of methods from the C++ classes such as \texttt{Triangulation, CellAccessor, TriaAccessor, Mapping, Manifold, GridTools} can now be invoked from Python. The accent was made on methods and functions that are widely used at a mesh preparation stage when a mesh is created and parameters related to the boundary, manifold and material identifiers are assigned.

A triangulation object can be read in or created using a number of simplistic geometries offered by the \texttt{GridGenerator}'s functions. Further information such as boundary, material and manifold identifiers can be assigned to cells and respective faces or edges (see Listing \ref{python_wrapper}). The introspective nature of the Python language makes it easy to infer the list of supported methods from the Python objects, for example by typing \texttt{dir(PyDealII.Release.Triangulation)}.

All triangulations created within the Python are serial. Once the mesh is designed, triangulation can be serialized along with the auxiliary information about possible refinement, boundaries, materials and manifolds. This object can be easily deserialized within a C++ program for subsequent production runs. Although saved triangulations are serial, it is possible to use them for construction of \texttt{parallel::shared, parallel::disrtibuted, and parallel::fullydistributed} (see also Section \ref{subsec:pft}) types of triangulations respecting the refinement and all the auxiliary information.

To facilitate the illustration of the new Python bindings, tutorial programs \href{https://github.com/dealii/dealii/blob/dealii-9.2/examples/step-49/step-49.ipynb}{step-49} and \href{https://github.com/dealii/dealii/blob/dealii-9.2/examples/step-53/step-53.ipynb}{step-53} were replicated in a form of the Jupyter notebooks.

Note that the current Python interface does not yet provide access to the actual \texttt{deal.II}'s finite element machinery, that is classes such as \texttt{DoFHandler, FE\_*, FEValues}, etc. It is envisaged that a progress towards this will be made for the next release.

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subsection~\ref{subsec:performance}, deal.II by default no longer
stores information for all processes on all processes, but only the
local information or the locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item
  \todo[inline]{What else is worth mentioning? Someone needs to go
    through the list of incompatible changes...}
\end{itemize}

@@

There are various ways to reference \dealii. To acknowledge the use of
the current version of the library, \textbf{please reference the present
document}. For up to date information and a bibtex entry for this document
see:
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For boundary element computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
   \item For uses of the \texttt{ParameterAcceptor} concept, the
     \texttt{MeshWorker::ScratchData} base class, and the
     \texttt{ParsedConvergenceTable} class:
     \cite{SartoriGiulianiBardelloni-2018-a};
   \item For uses of the particle functionality in \dealii{}: \cite{GLHPB18}.
\end{itemize}

>>>>

The class \texttt{VectorizedArray<Number>} is a key component to achieve the high
node-level performance of the matrix-free algorithms in deal.II~\cite{KronbichlerKormann2012, KronbichlerKormann2019}. It is a wrapper
class around a short vector of $n$ entries of type \texttt{Number} and maps
arithmetic operations to appropriate single-instruction/multiple-data (SIMD)
concepts by intrinsic functions.
The class \texttt{VectorizedArray} has been made more user-friendly in this release by making
it compatible with the STL algorithms found in the header \texttt{<algorithm>}.
The length of the  vector can now be queried by  \texttt{VectorizedArray::size()} and its underlying number type by \texttt{VectorizedArray::value\_type}.
Furthermore, the \texttt{VectorizedArray} class now supports range-based iteration over its entries.

In previous \dealii{} releases, the
vector length was set at compile time of the library to match the highest
value supported by the given processor architecture.
Now, a second optional template argument
can be specified as \texttt{VectorizedArray<Number, size>}, where \texttt{size} explicitly controls
the vector length within the capabilities of a particular instruction set.
(A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.)
This allows users to select the vector length/ISA and,
as a consequence, the number of cells to be processed at once in matrix-free
operator evaluations. For example, the deal.II-based
library \texttt{hyper.deal}~\cite{munch2020hyperdeal}, which solves the 6D Vlasov--Poisson equation with high-order
discontinuous Galerkin methods (with more than a thousand degrees of freedom per cell), constructs a tensor product of two \texttt{MatrixFree} objects of different SIMD-vector
length in the same application and benefits---in terms of performance---by the possibility of decreasing the number of cells processed by a single SIMD instruction.

\begin{table}
\caption{\it Supported vector lengths of the class \texttt{VectorizedArray} and
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2/AltiVec \\
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\
\bottomrule
\end{tabular}

\caption{\it Comparison of relevant SIMD-related classes in deal.II and \texttt{C++23}.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (\texttt{C++23})} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

The new interface of \texttt{VectorizedArray} also enables replacement
by any type with a matching interface. Specifically, this prepares
\dealii{} for the \texttt{std::simd} class that is slated to become
part of the \texttt{C++23} standard.
Table~\ref{tab:simd} compares the deal.II-specific SIMD classes and
the equivalent \texttt{C++23} classes. These changes also prepare for specialized
code paths exploiting
vectorization within an element, see~\cite{KronbichlerKormann2019}.

@@

For this release, the most noteworthy improvements in GPU support are the
simplification of the kernel written by user, improvement of error messaging,
and overlapping of computation and communication when using CUDA-aware MPI with
the matrix-free framework.

In order to simplify user code, we now recompute
local degree of freedom and quadrature point indices instead of having the user
keeping track of them. A new option to overlap computation and communication is
now available when using CUDA-aware MPI and matrix-free. The underlying idea is
that only the degrees of freedom (DoFs) on the boundary of the local domain
require communication. Before evaluating the matrix-free operator at these
degrees of freedom, we need to communicate ghost DoFs from other
processors.  Similarly once the operator has been evaluated, we need to update
the resulting global vector with values from other processors. The strategy that
we are now using consists in splitting the DoFs into three groups: one group of DoFs
that are on the local boundary and two groups each owning half of the interior
DoFs. When evaluating the matrix-free operator, we start the MPI communication
to get the ghosted DoFs and evaluate the operator on one of the two interior
DoFs group. When the evaluation is done, we wait for the MPI
communication to be over, and
then evaluate the operator on the boundary DoFs group. When this evaluation is
completed, we start the communication to update the global vector, we evaluate the
operator on the last group of DoFs, and finally wait for the MPI
communication to finish.

@@

Certain types of quantities in a simulation are constants fully known
at compile time. They can be pre-calculated and stored in the
compiled executable in order to avoid unnecessary initialization during
runtime. C++11 and later standards enables such computations by
marking variables and functions with the \texttt{constexpr} keyword.

This optimization is now enabled for the class templates
\texttt{Tensor} and \texttt{SymmetricTensor}.
For instance, the linear mechanical constitutive model for isotropic elastic solids
uses a constant fourth-order elasticity tensor
$\mathbb{C} = \lambda \boldsymbol{I} \otimes \boldsymbol{I} + 2 \mu \mathbb{I}$
which does not depend on the current state of strain.
This tensor can now be statically initialized by defining it as
\texttt{constexpr SymmetricTensor<4, dim>}.
As another example, the lattice vectors in a crystal plasticity model are generally
constant and known during compilation time, enabling their efficient definition as
\texttt{constexpr Tensor<1, dim>}.

Declaring variables, functions, and methods as \texttt{constexpr}
is a C++11 feature that was later expanded by the C++14 standard.
Thus, parts of the \texttt{constexpr} support in \dealii{} depend on the C++
standard supported by the compiler used to install the library.

The next release of \dealii{} will require compiler support for the C++14 standard.

@@

In addition, there are a number of new tutorial programs:
\begin{itemize}
\item \texttt{step-47} is a new program that solves the biharmonic
  equation $\Delta^2 u = f$ with
  ``clamped'' boundary condition given by $u=g, \partial u/\partial
  n=h$. This program is based on the $C^0$ interior
  penalty ($C^0$IP) method for fourth order problems
  \cite{Brenner2005}. In order to overcome
  shortcomings of classical approaches, this method uses $C^0$ Lagrange finite
  elements and introduces ``jump'' and ``average'' operators on
  interfaces of elements that penalize the jump of the gradient of the
  solution in order to obtain convergence to the $H^2$-regular
  solution of the equation.

  The $C^0$IP approach is a modern alternative to classical methods that
  use $C^1$-conforming elements such as the Argyris
  element, the Clough-Tocher element and others, all developed in the
  late 1960s. From a twenty-first century perspective, they can only be
  described as bizarre in their construction. They are also exceedingly
  cumbersome to implement if one wants to use general meshes. As a
  consequence, they have largely fallen out of favor and deal.II currently
  does not contain implementations of these shape functions.

@@

\item \texttt{step-58} is a program that solves the nonlinear
  Schr{\"o}dinger equation, which in non-dimensional form reads
  \begin{align*}
  - i \frac{\partial \psi}{\partial t}
  - \frac 12 \Delta \psi
  + V \psi
  + \kappa |\psi|^2 \psi
  &= 0,
  \end{align*}
  augmented by appropriate initial and boundary conditions and using
  an appropriate form for the potential $V=V(\mathbf x)$. The
  tutorial program focuses on two specific aspects for which this
  equation serves as an excellent test case: (i) Solving
  complex-valued problems without splitting the equation into its
  real and imaginary parts (as \texttt{step-29} does, for
  example). (ii)~Using operator splitting techniques. The equation is
  a particularly good test case for this technique because the only
  nonlinear term, $\kappa |\psi|^2 \psi$, does not contain any
  derivatives and consequently forms an ODE at each node point, to be
  solved in each time 
  step in an operator splitting scheme (for which, furthermore, there
  exists an analytic solution), whereas the remainder of the
  equation is linear and easily solved using standard finite element
  techniques.

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{python_mesh.png}
\caption{\it The mesh generated by the Python code shown in the main
  text. Cells are colored by material id.}
\label{fig:pymesh}
\end{figure}

Initial support for Python has existed in \dealii{} since version
9.0. The present release significantly extends the Python
interface. Specifically, a large number of methods from classes such
as \texttt{Triangulation, CellAccessor, TriaAccessor, Mapping,
  Manifold, GridTools} can now be invoked from Python. We have focused
on methods and functions that are widely used when a mesh is created
and parameters related to the boundary, manifold, and material
identifiers are assigned. The following listing gives an idea of how
such code looks:
\begin{python}
import PyDealII.Release as dealii

@@

triangulation.execute_coarsening_and_refinement()
\end{python}
The mesh that results from this code is shown in Fig.~\ref{fig:pymesh}.

All triangulations created from within Python are serial. However,
once the mesh is designed, the triangulation can be serialized along
with the auxiliary information about possible refinement, boundaries,
materials and manifolds. This object can be easily deserialized within
a C++ program for subsequent production runs. Furthermore, such a
serialized triangulation can also be used in the construction of
\texttt{parallel::shared}, \texttt{parallel::disrtibuted}, and
\texttt{parallel::fullydistributed} triangulations (see also Section~\ref{subsec:pft}).

To facilitate the illustration of the new Python bindings, tutorial programs \href{https://github.com/dealii/dealii/blob/dealii-9.2/examples/step-49/step-49.ipynb}{step-49} and \href{https://github.com/dealii/dealii/blob/dealii-9.2/examples/step-53/step-53.ipynb}{step-53} were replicated as Jupyter notebooks.

The introspective nature of the Python language makes it easy to infer
the list of supported methods from the Python objects, for example by
typing \texttt{dir(PyDealII.Release.Triangulation)}. 
The current Python interface does not yet provide access to \dealii{}'s finite element machinery, i.e., classes such as \texttt{DoFHandler, FE\_*, FEValues}, etc.

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item Two functions that provide information about all processes,
  namely
  \begin{itemize}
 \item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
 \item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
  \end{itemize}
have been deprecated. As discussed in
Subsection~\ref{subsec:performance}, deal.II by default no longer
stores information for all processes on all processes, but only
local or locally-relevant information. On the other
hand, if necessary, global information can still be computed using,
for example, calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item
  \todo[inline]{What else is worth mentioning? Someone needs to go
    through the list of incompatible changes...}
\end{itemize}

@@

There are various ways to reference \dealii. To acknowledge the use of
the current version of the library, \textbf{please reference the present
document}. For up to date information and a bibtex entry
see
\begin{center}
 \url{https://www.dealii.org/publications.html}
\end{center}

The original \texttt{\dealii} paper containing an overview of its
architecture is \cite{BangerthHartmannKanschat2007}. If you rely on
specific features of the library, please consider citing any of the
following:
\begin{multicols}{2}
  \vspace*{-36pt}
  \begin{itemize}
 \item For geometric multigrid: \cite{Kanschat2004,JanssenKanschat2011,ClevengerHeisterKanschatKronbichler2019};
 \item For distributed parallel computing: \cite{BangerthBursteddeHeisterKronbichler11};
 \item For $hp$~adaptivity: \cite{BangerthKayserHerold2007};
  \item For partition-of-unity (PUM) and enrichment methods of the
    finite element space: \cite{Davydov2016};
 \item For matrix-free and fast assembly techniques:
   \cite{KronbichlerKormann2012,KronbichlerKormann2019};
 \item For computations on lower-dimensional manifolds:
   \cite{DeSimoneHeltaiManigrasso2009};
 \item For curved geometry representations and manifolds:
   \cite{HeltaiBangerthKronbichlerMola2019};
   \vfill\null  \columnbreak
 \item For integration with CAD files and tools:
   \cite{HeltaiMola2015};
 \item For boundary element computations:
   \cite{GiulianiMolaHeltai-2018-a};
 \item For \texttt{LinearOperator} and \texttt{PackagedOperation} facilities:
   \cite{MaierBardelloniHeltai-2016-a,MaierBardelloniHeltai-2016-b};
 \item For uses of the \texttt{WorkStream} interface:
   \cite{TKB16};
 \item For uses of the \texttt{ParameterAcceptor} concept, the
   \texttt{MeshWorker::ScratchData} base class, and the
   \texttt{ParsedConvergenceTable} class:
   \cite{SartoriGiulianiBardelloni-2018-a};
 \item For uses of the particle functionality in \dealii{}:
   \cite{GLHPB18}.
   \vfill\null  
\end{itemize}
\end{multicols}
